---
title: "Test Page for Everyday Listening"
output: github_document
---

## My playlists

Of all my playlists on Spotify, there are two that I like to listen to the most. One is called *Chill* and the other is called *Karaoke*. *Chill* contains a lot of songs to relax to. I think these are slower, acoustic songs, possibly played in minor more often than major. I think the songs in *Karaoke* are more energetic, maybe easier to dance to and also louder. Let's see if the Spotify API would say the same.

```{r, include = FALSE}
library(tidyverse)
library(spotifyr)
source('spotify.R')
```

```{r, include = FALSE}
chill = get_playlist_audio_features('11143302739','0TIMetHqr6J6S6QR19x8yi') 
karaoke = get_playlist_audio_features('11143302739','3sJGjIN1wa9KszybCcj0hB') 

spotify_features <-
  ## Use the tribble() function to give one-word labels for your playlists, e.g.,
  ## type and subtype, or group member and year, plus the URIs for the Spotify
  ## user and playlist. Often the user is just 'spotify'.
  tribble(
    ~type, ~user, ~playlist,
    'Chill', '11143302739', '0TIMetHqr6J6S6QR19x8yi',
    'Karaoke', '11143302739', '3sJGjIN1wa9KszybCcj0hB'
  ) %>% 
  ## This line downloads the features from Spotify.
  mutate(features = map2(user, playlist, get_playlist_audio_features)) %>% 
  ## Use the select() function to keep your label columns, plus the features.
  select(type, features) %>% 
  ## This line expands the features into a single table.
  unnest(features)
```

```{r}
spotify_features %>% 
  ## Try grouping by group member and/or year.
  group_by(type) %>% 
  ## Try different features and different summary functions.
  summarise(Tempo=mean(tempo), Acousticness=mean(acousticness), Mode=mean(mode), Energy=mean(energy), Danceability=mean(danceability), Loudness=mean(loudness))
```

